A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-10-04 sections/methodology/main.tex
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

Th problem defined in section \ref{sec:model_overview} describes a normal-form
game between the decision makers of two queueing systems and a third player that 
decides how to distribute individuals to the systems.
The strategy space of the two queueing systems is defined as the possible values
that the threshold parameter can take \(T_i \in (1, N_i)\).
Then, the distributor has to decide on the proportion of individuals to send to 
each queueing system \(p_A \text{ and } p_B\), where \(p_A, p_B \in [0, 1] \)
and \(p_A + p_B = 1\).
Figure \ref{fig:imperfect_info_game} form section \ref{sec:model_overview} 
shows a diagrammatic representation of the game to be played and the decisions 
to be made.
As described in section \ref{sec:model_overview} queueing system \(A\) decides
on a strategy, then queueing system \(B\) chooses its own threshold, unaware 
of the first queueing system's choice.
Finally, the distributor makes its choice based on the strategies that the 
queueing systems chose to play.

The problem can be formulated by 3 matrices; the two payoff matrices of the 
normal form game and the routing matrix.
The payoff matrices and their utilities are defined by equations 
(\ref{eq:payoff_entry}) and (\ref{eq:payoff_matrices}) in section 
\ref{sec:model_overview}.

The routing matrix holds the values \((p_A, p_B)\) which are the proportion 
of class 2 individuals to send to queueing system \(A\) and \(B\).
Each pair \((p_A, p_B)\) can be calculated using equation 
(\ref{eq:obj_distributor}).
Equation \ref{eq:obj_distributor} is defined and explained in section 
\ref{sec:model_overview}.
Thus, using equation \ref{eq:obj_distributor} for all possible sets of 
thresholds we can get the full routing matrix that consists of the proportions
to send to queueing system A (\(p_A\)) and to queueing system B (\(p_B\)).

@@

The values of \(p_A\) and \(p_B\) that satisfy equation 
(\ref{eq:obj_distributor_1_1}) can be found by using Brent's bisection 
algorithm~\cite{brent1973algorithms}.
The calculated value of \(p_A\) corresponds to the entry on the first row and 
first column of the routing matrix:

@@

Having calculated the payoff matrices \(A\) and \(B\), several algorithms can 
be used to help us find the Nash equilibrium of the game. 
The Nash equilibrium is the point of the game were both players have no 
incentive to deviate from their played strategies \cite{kreps1989nash}.
In other words their chosen strategies are a best response to each other.

The Lemke-Howson algorithm is used to get all Nash equilibria of the game 
\cite{LemkeHowson}.
Lemke-Howson uses best response polytopes to get one of the Nash equilibrium of
the game. 
By iterating over all possible dropped labels of the best response polytope all
Nash equilibria can be acquired.
All game theoretic calculations were done in Python using the Nashpy library 
\cite{axelrodproject}.

@@

In order to analyse the strategies played by the two EDs, the learning algorithm
asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
The two players are treated as two separate populations where each 
individual in the population is assigned a strategy.
As the game progresses the proportion of each player playing each strategy 
changes based on their previous interactions.
The fitness of each strategy is defined as:

@@

Here, \(x \in \mathbb{R}^{m \times 1} \) and
\(y \in \mathbb{R}^{n \times 1}\) correspond to the proportion of individuals 
that play each strategy on the two populations.
Similarly, the average fitness of each strategy is defined as:
\begin{equation}
    \phi_x = f_x x^T, \quad \phi_y = f_y y
\end{equation}

>>>>

Th problem defined in section \ref{sec:model_overview} describes a normal-form
game between the decision makers of two queueing systems and a third player that 
decides how to distribute individuals to the systems.
The strategy space of the two queueing systems is defined as the possible values
that the threshold parameter can take \(T_i \in (1, N_i)\).
Then, the distributor has to decide on the proportion of individuals to send to 
each queueing system \(p_A \text{ and } p_B\), where \(p_A, p_B \in [0, 1] \)
and \(p_A + p_B = 1\).
Figure \ref{fig:imperfect_info_game} form section \ref{sec:model_overview} 
shows a diagrammatic representation of the game to be played and the decisions 
to be made.
As described in section \ref{sec:model_overview} queueing system \(A\) decides
on a strategy, at the same time, queueing system \(B\) chooses its own threshold, unaware 
of the first queueing system's choice.
Finally, the distributor makes its choice based on the strategies that the 
queueing systems chose to play.

The utilities to each player can be represented by 3 matrices; the two payoff matrices of the 
normal form game and the routing matrix.
The payoff matrices and their utilities are defined by equations 
(\ref{eq:payoff_entry}) and (\ref{eq:payoff_matrices}) in section 
\ref{sec:model_overview}.

The routing matrix holds the values \((p_A, p_B)\) which are the proportion 
of class 2 individuals to send to queueing system \(A\) and \(B\).
Each pair \((p_A, p_B)\) can be calculated using equation 
(\ref{eq:obj_distributor}) and is essentially
a best response to the actions of the queueing systems.
Equation \ref{eq:obj_distributor} is defined and explained in section 
\ref{sec:model_overview}.
Thus, using equation \ref{eq:obj_distributor} for all possible sets of 
thresholds we can get the full routing matrix that consists of the proportions
to send to queueing system A (\(p_A\)) and to queueing system B (\(p_B\)).

@@

The values of \(p_A\) and \(p_B\) that satisfy equation 
(\ref{eq:obj_distributor_1_1}) are here found numerically using Brent's bisection
algorithm~\cite{brent1973algorithms}.
The calculated value of \(p_A\) corresponds to the entry on the first row and 
first column of the routing matrix:

@@

Having calculated the payoff matrices \(A\) and \(B\), several algorithms can 
be used to measure some form of emergent behaviour.
One possibility would be to compute the Nash equilibrium
which is the point of the game were both players have no 
incentive to deviate from their played strategies \cite{kreps1989nash}.
In other words their chosen strategies are a best response to each other.

Computation of Nash equilibria can be done relatively efficiently using the Lemke Howson algorithm
\cite{LemkeHowson}.
Lemke-Howson uses best response polytopes to get one of the Nash equilibrium of
the game. 
Other algorithms exists that will compute all Nash equilibria but 
for large games the computational complexity becomes problematic.
All game theoretic calculations were done in Python using the Nashpy library 
\cite{axelrodproject}.

@@

Another approach to measuring emergent behaviour is to consider 
the emergence itself and not just stable end points. 
Indeed, some Nash equilibria might not arise naturally. Thus, in order to analyse the strategies played by the two EDs, the learning algorithm:
asymmetric replicator dynamics is used \cite{asymmetricreplicatordynamics}.
The two players are modelled as two separate populations where each 
individual in the population is assigned a strategy.
As the game progresses the proportion of each player playing each strategy 
changes based on their previous interactions.
The fitness of each strategy is defined as:

@@

Here, \(x \in \mathbb{R}^{m \times 1} \) and
\(y \in \mathbb{R}^{n \times 1}\) correspond to the proportion of individuals 
that play each strategy in each population.
Similarly, the average fitness of each strategy is given by:
\begin{equation}
    \phi_x = f_x x^T, \quad \phi_y = f_y y
\end{equation}
